Compute Servers for Teaching Big Data

### 2025-01-07 paper.tex
.

>>>>

The class is called `Big Data'.
For this term to have any meaning, we need to define what we mean by `big'.
For the purposes of this class, a `big' data set is one that is large enough that one cannot load the entire data set into a laptop's memory at once.
Once a data set is this large, it's not possible to simply load the whole thing and start working using R or Python.
My goal is to choose data sets that are comfortably over this threshold, such that the techniques we're learning are motivated, but not gratuitously large such that answering a basic question takes many hours.
Practically speaking, from 2019 until the present I try to choose data sets that are on the order of 10 or 100 GB.
